\TheTitle

### 2019-07-25 Paper1/introduction.tex
minor fixes introduction

In this paper, we investigate intrusive methods for steady problems and compare them against collocation methods. For both steady and unsteady problems, we use adaptivity: 
\begin{itemize}
\item The intrusive nature of SG and IPM can be used to locally increase the number of moments whenever the solution has a complex structure in the random variable (as well as decrease the number of moments if not).
\end{itemize}
The steady setting provides different opportunities to take advantage of features of intrusive methods: 
\begin{itemize}
\item When using adaptivity, one can perform a large number of iteration to the steady state solution on a low number of moments and increase the maximal refinement level when the distance to the steady state has reached a specified barrier. Consequently, a large number of iterations will be performed by a cheap method, i.e. we can reduce numerical costs. 
\item Accelerate the convergence to the steady state IPM solution by applying IPM as a post-processing step for collocation methods: We converge the moments of the solution to a steady state with an inaccurate, but cheap collocation method and then use the resulting collocation moments as starting values for an expensive but accurate intrusive method such as IPM, which we then again converge to steady state. 
\item Compute inexact dual variables \eqref{eq:dualProblem} for IPM: Since the moments during the iteration process are inaccurate, i.e. they are not the correct steady state solution, we propose to not fully converge the dual iteration, which computes \eqref{eq:dualProblem}. Consequently, the dual variables and the moments are converges simultaneously to their steady state, which is similar to the idea of one-shot optimization in shape optimization \cite{hazra2005aerodynamic}.
\end{itemize}

The effectiveness of these acceleration ideas are tested by comparing results with stochastic-Collocation for the uncertain NACA test case as well as a bent shock tube problem. Furthermore, we present a semi-intrusive method, which facilitates the task of implementing general intrusive methods. The method only requires the numerical flux of the deterministic problem (as well as an entropy if IPM is used). We thereby provide the ability to recycle existing implementations of deterministic solvers. Our numerical studies show the following main results:
\begin{itemize}
\item The standard IPM method cannot compete with SC and SG. However when using the discussed acceleration techniques, IPM reaches a given accuracy with the shortest run time.
\item Comparing SG with IPM, one observes that for the same number of unknowns, SG yields more accurate expectation values, whereas IPM leads to better variance approximations.
\item By studying aliasing effects, we show that SC requires a higher number of unknowns than intrusive methods, even for one spatial dimension to reach the same accuracy level.
\end{itemize}

>>>>

In this paper, we propose acceleration techniques for intrusive methods and compare them against stochastic-Collocation. For steady and unsteady problems, we use adaptivity: 
\begin{itemize}
\item The intrusive nature of SG and IPM can be used to locally increase the number of moments whenever the solution has a complex structure in the random variable (as well as decrease the number of moments if not).
\end{itemize}
A steady problem provides different opportunities to take advantage of features of intrusive methods: 
\begin{itemize}
\item When using adaptivity, one can perform a large number of iteration to the steady state solution on a low number of moments and increase the maximal refinement level when the distance to the steady state has reached a specified barrier. Consequently, a large number of iterations will be performed by a cheap method, i.e. we can reduce numerical costs. 
\item Accelerate the convergence to the steady state IPM solution by applying IPM as a post-processing step for collocation methods: We converge the moments of the solution to a steady state with an inaccurate, but cheap collocation method and then use the resulting collocation moments as starting values for an expensive but accurate intrusive method such as IPM, which we then again converge to steady state. 
\item Compute inexact dual variables \eqref{eq:dualProblem} for IPM: Since the moments during the iteration process are inaccurate, i.e. they are not the correct steady state solution, we propose to not fully converge the dual iteration, which computes \eqref{eq:dualProblem}. Consequently, the dual variables and the moments are converges simultaneously to their steady state, which is similar to the idea of one-shot optimization in shape optimization \cite{hazra2005aerodynamic}.
\end{itemize}

The effectiveness of these acceleration ideas are tested by comparing results with stochastic-Collocation for the uncertain NACA test case as well as a bent shock tube problem. Our numerical studies show the following main results:
\begin{itemize}
\item The standard IPM method cannot compete with SC and SG. However when using the discussed acceleration techniques, IPM reaches a given accuracy with the shortest run time.
\item Comparing SG with IPM, one observes that for the same number of unknowns, SG yields more accurate expectation values, whereas IPM leads to better variance approximations.
\item By studying aliasing effects, we show that SC requires a higher number of unknowns than intrusive methods, even for one spatial dimension to reach the same accuracy level.
\end{itemize}
Furthermore, we present a semi-intrusive method, which facilitates the task of implementing general intrusive methods. The method only requires the numerical flux of the deterministic problem (as well as an entropy if IPM is used). We thereby provide the ability to recycle existing implementations of deterministic solvers.
